Identifying the Tissue of Origin of Extracellular Vesicles Using RNA Expression Signatures

### 2015-08-28 poster/poster.Rnw
start loading specific genes into poster

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
#opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
library("data.table")
library("ggplot2")
library("reshape2")
library("proto")
@

@@

>>>>

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
#opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
library("data.table")
library("ggplot2")
library("reshape2")
library("proto")
library("xtable")
@

<<load.data,echo=FALSE,results="hide",warning=FALSE,cache.extra=tools::md5sum("../tissue_specific_expression/tissue_specific_markers")>>=
load("../tissue_specific_expression/tissue_specific_markers")
tissue.specific.genes <- data.table(tissue.specific.genes)
@

@@

  \block{Uterus Specific Genes}{

<<uterus.specific.markers.table,results="asis",echo=FALSE>>=
temp <- tissue.specific.genes[tissue=="uterus",list(gene,specificity)]
setnames(temp,c("Gene","Tissue Specificity"))
print(xtable(temp,
             caption="Uterus specific genes",label="tab:uterus_specific_genes"),
      floating=FALSE,
      include.rownames=FALSE,
      )
rm(temp)
@ 
}

\column{0.3}
  \block{Placenta Specific Genes}{

<<placenta.specific.markers.table,results="asis",echo=FALSE>>=
temp <- tissue.specific.genes[tissue=="placenta" & gi.max > 100,list(gene,specificity)]
setnames(temp,c("Gene","Tissue Specificity"))
print(xtable(temp,
             caption="Placenta specific genes",label="tab:placenta_specific_genes"),
      floating=FALSE,
      include.rownames=FALSE,
      )
rm(temp)
@ 
}
